### 2017-09-15 monograph/thesis/postexto/abstracts.tex
Created the annex postexto/abstracts.tex to save the references'
abstracts.

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\lang{Introduction}{Introdução}}

\lang
{
    % TODO, put reference for this
    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{industrialApplication}

    % TODO, put reference for this
    But entering the universe of good practices, there are many things for
    discoursing. So in this work implementation tool called `Object Beautifier'
    specifically dedicates on how to perform the best layout/display of
    programming code on the computer screen, so that maximize and facilitate the
    understanding of same. Therefore, allowing the programmer to disperse more
    tempe thinking about its coding algorithms problem, other than trying to
    decipher the information that is presented to it on the screen through
    infinit different code layouts. \cite{programIndentation}

    % TODO, put reference for this
    Within this work\s area, we need to also think long and hard about how to
    share the programming code of the programmers among you. Now, the problem of
    human diversity, like all big scientific questions -- how do you explain
    something like that -- It can be broken down into sub-questions. It happens
    many times, which is a good practice for a `Programmer A', is not the same
    to another `Programmer B'. For example, imagine some code where a programmer
    decided to put before each `if' statement, a blank line. It is therefore
    expected that whenever we see a blank line we can potentially find a
    matching `if', which can be considered a quite useful pattern matching as
    empty line may call better your attention. \cite{independentFramework}

    % TODO, put reference for this
    But again this is something heavily dependent of what each one learning
    through their life time. Imagine another programmer do not liked this rule,
    and when he was writing your code involving an `if', he did not put such
    blank line another programmer is expecting. So when the first programmer
    start reading its the code and look for `if', he will be expecting for blank
    lines before its if\s. But will lose some time searching until realize
    another programmer does not put them, or perhaps he forgot to insert them.
    \cite{architectureFormatting}

    % TODO, put reference for this
    These differences are due to the diversity of ways we learn programming,
    i.e., to the ways we are used to doing coding, as much as the abilities and
    objectives of every programmer developed. Hence, nowadays it becomes a big
    problem because we increasingly need more and more programmers working
    together developing several and diverse computing systems. Where the latter
    is due to the fact of the complexity of computer systems growing
    increasingly, therefore over requiring programmers working and sharing their
    codes and ideas. \cite{prettyPrinting}

    % TODO, put reference for this
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain-text' mode. Since for code sharing, it is vital for you
    to use a versioning control system which enable project manager\s and
    programmers themselves, take control of their code changes. It does allow to
    easily perform the tracking of code changes and allow you to better
    understand what each programmer is doing every time he formalizes a change
    in the code through a `commit', as in `git' systems for example.
    \cite{massMaintenance}

    % TODO, put reference for this (ref coding\_horror)
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did. Hence, if every
    programmer re-writes the history making changes like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines (ref find\_some). \cite{legacyAssets}

    % TODO, put reference for this
    Talking about the last thing pointed out, we could also think about an
    approach to creating a new version control system which focuses only on
    significant changes to the code, while reviewing code changes. However, this
    approach could not be ideal, as for example, it would allow programmers to
    start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code
    re-adding new lines before each one of your beloved if\s, just because some
    night shift programmer had just removed them? \cite{softwarePortfolio}

    \section{Goals}

    Establish relationships between good programming practices and efficiency in
    programming, in addition to a new tool to support programmers in order to
    automate the long and diverse programming process in teams of developers
    with different programming `best practices'. \cite{pushdownAutomata}

    \subsection{Specific Goals}

    \begin{enumerate}
        \item A study on universal programming tools, which from a single
        software, to work well behaved accross all programming languages.
        Moreover, explain the differences for other softwares and the beneficits
        of a unique tool, instead of several heavly different ones.

        \item Define, determine and classify which one are good programming
        practices and perform an in-depth study on the good practices on visual
        layout area, also known as code `Beautifying'.

        \item A study on the variety of existing tools for the support of good
        programming practices, beyond a comparative analysis between them,
        determining their weaknesses and strengths.

        \item The definition of a flow pattern of development allowing teams of
        developers with different programming best practices, to work without
        intervene with each other up to start wars of `best good practices'.

        \item Propose a unique tool that allowing several and distinct
        programming `best practices'being implemented in several programming
        languages, which can be configured and set accordingly to their wishes.
    \end{enumerate}

    \section{Search Method}

    The work will be based on research in articles, books, theses,
    dissertations, trusted authors websites, and through new demonstrated
    evidences based on arguments in the monograph evolution road. Also, present
    results after building a new tool which proposes a solution for the problems
    presented and detailed. \cite{aspectOriented}

    In this proposal last chapter which lies in the topic
    \autoref{sec:implementation}, there is a series of weblinks and references
    preselected and may be used in the release build of this work. Noticing the
    texts of the last section probably will end up gradually moved to the first
    section of the text where there is the theoretical research, while
    correlated research are incorporated in the main written work.
    \cite{aspectOrientationReview}

    Moreover, at the end of the first part of this work, the completion of the
    subject entitled of Course Conclusion Work 1, leaving only the information
    for the implementation of the proposed tool to be implemented in the second
    part of this named thesis on \nameref{sec:implementation}.

}
{
    % Portuguese
    \input{chapters/introdução}
}

>>>>

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\lang{References' Abstracts}{Resumos das Referências}}

\begin{englishtext}
\begin{enumerate}

    \item In this paper we argue that there is a necessity for automating modifications to legacy assets.
    We propose a five layered process for the introduction and employment of tool support that
    enables automated modification to entire legacy systems. Furthermore, we elaborately discuss
    each layer on a conceptual level, and we make appropriate references to sources where technical
    contributions supporting that particular layer can be found. We sketch the perspective that more
    and more people working in the software engineering area will be contributing to working on
    existing systems and/or tools to support such work. \cite{legacyAssets}

\end{enumerate}
\end{englishtext}
